Damage localization based on vibrations

### 2017-04-04 rapport/paper.tex
small collection

The purpose of this work is the analysis of a particular data-driven damage localization method,
 namely the FRF interpolation method \cite{dilena2015damage}. Our contribution is the development of a simulation to obtain acceleration measurement (which can run on several structures), a proposition of a variant of the FRF interpolation method, and the statistical analysis of the two methods.
This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
then in section III we present different models of vibrating structures required for what happens next. In section IV,  we talk about the localization using FRF interpolation method, in section V we detail our simulation used to obtain data and, finally, the experiences and its results in section VI.

@@

We have implemented a simulation to obtain the data used to check the methods of localization. To explain it, we detil here the following system we used for our experiences: $n$ masses, connected
through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure (\ref{springs})).

@@

To test the localization, we have to make a thresold for each sensor. We want that a computed error taller than the threshold on one sensor is equivalent to have a damage on this sensor. With the FRF interpolation method, we have compute two thresholds from 100 experiments with the undameged state. The first is the error just below the maximum of the 100 errors computed. The second is computed from the statistics of the 100 errors computed: we suppose that the probability of the error follow a normal distribution, and we choose the threshold at 95\% of this distribution.

From now on, the majority of the figures will show four curves:
\begin{itemize}
\item in blue (deep): results for the FRF interpolation method with a threshold at 99\% of the reference errors
\item in green: results for the FRF interpolation method with a threshold at 95\% of the reference distribution
\item in red: results for the FRF difference method with a threshold at 99\% of the reference errors
\item in blue (light): results for the FRF difference method with a threshold at 95\% of the reference distribution
\end{itemize}

To disting the two methods with the two thresholds, we denote them with the color initials: the first one BD, the second one G, the third one R and the last one BL.

@@

Figure(\ref{detect}) presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7). We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that BL is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%. However, at 15\% of damage, it's BD and G which are the best, with 100\% of detection. BL reaches 100\% of detection at 20\% of damage, and R reaches it at 30\% of damage. Here, R seems to be the worst.

>>>>

The purpose of this work is the analysis of a particular data-driven damage localization method,
 namely the FRF interpolation method \cite{dilena2015damage}. Our contribution is the development of a simulator to obtain acceleration measurement of different structures, a proposition of a variant of the FRF interpolation method, and a statistical analysis of the two methods.

This paper is organized as follows: In section II we  present the existing methods (model-based and data driven methods),
then in section III we present different models of vibrating structures required for what happens next. In section IV,  we talk about the localization using FRF interpolation method, in section V we detail our simulation used to obtain data and, finally, the experiences and its results in section VI.

@@

We have implemented a simulation to obtain the data used to check the methods of localization. To explain it, we detail here the following system we used for our experiences: $n$ masses, connected
through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure (\ref{springs})).

@@

To test the localization, we have to make a threshold for each sensor. We want that a computed error bigger than the threshold on one sensor is equivalent to have a damage on this sensor. With the FRF interpolation method, we have compute two thresholds from 100 experiments with the undamaged state. The first is the error just below the maximum of the 100 errors computed. The second is computed from the statistics of the 100 errors computed: we suppose that the probability of the error follow a normal distribution, and we choose the threshold at 95\% of this distribution.

From now on, the majority of the figures will show four curves:
\begin{itemize}
\item in dark blue: results of the FRF interpolation method with a threshold at 99\% of the reference errors
\item in green: results of the FRF interpolation method with a threshold at 95\% of the reference distribution
\item in red: results of the FRF difference method with a threshold at 99\% of the reference errors
\item in blue : results of the FRF difference method with a threshold at 95\% of the reference distribution
\end{itemize}

To disting the two methods with the two thresholds, we denote them with the color initials: the first one DB, the second one G, the third one R and the last one B.

@@

Figure(\ref{detect}) presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7). We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that B is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%. However, at 15\% of damage, it's DB and G which are the best, with 100\% of detection. B reaches 100\% of detection at 20\% of damage, and R reaches it at 30\% of damage. Here, R seems to be the worst.
